\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[english]{babel} 
\usepackage[margin=2.5cm]{geometry}
\geometry{a4paper}
\usepackage{longtable}
\usepackage{subfigure}
\usepackage[normalem]{ulem}


\usepackage{array,arydshln}
%\setlength\dashlinedash{0.2pt}
%\setlength\dashlinegap{4.5pt}
%\setlength\arrayrulewidth{0.2pt}
\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\arraybackslash}m{#1}}

\usepackage{multicol}
\usepackage[table]{xcolor}
\usepackage{todonotes}
\usepackage{menukeys}

%----------------------------KODE START---------------------------------------
%\usepackage{listings}
%\usepackage{color}
%\usepackage[usenames,dvipsnames,table]{xcolor}
%\definecolor{gray}{rgb}{0.5,0.5,0.5}
%\definecolor{mauve}{rgb}{0.58,0,0.82}
%\lstset{
%  basicstyle=\footnotesize,
%  numbers=left,
%  numberstyle=\tiny\color{gray},
%  stepnumber=1,
%  numbersep=10pt,
%  backgroundcolor=\color{white},
%  showspaces=false,               % show spaces adding particular underscores
%  showstringspaces=false,         % underline spaces within strings
%  showtabs=false,                 % show tabs within strings adding particular underscores
%  frame=single,                   % adds a frame around the code
%  rulecolor=\color{black},        
%  tabsize=4,
%  captionpos=b,                   % sets the caption-position to bottom
%  breaklines=true,                % sets automatic line breaking
%  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
%  title=\lstname,                   % show the filename of files included with \lstinputlisting;
                                  % also try caption instead of title
%  keywordstyle=\color{mauve},          % keyword style
%  commentstyle=\color{Maroon},       % comment style
%  stringstyle=\color{BlueViolet},         % string literal style
%  escapeinside={\%*}{*)},            % if you want to add LaTeX within your code
%  morekeywords={*,...},              % if you want to add more keywords to the set
%  deletekeywords={...}              % if you want to delete keywords from the given language
%}
%----------------------------KODE SLUT----------------------------------------


\setlength\parindent{0pt} % Makes \noindent standard
\usepackage{graphicx} 
\usepackage{sidecap}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{float} 
\usepackage{wrapfig} % Allows in-line images if needed
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\hypersetup{colorlinks=false,hidelinks, citecolor=black, urlcolor=black}
\usepackage{csquotes}
\usepackage{comment}
\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}

\usepackage[dot, autosize, outputdir="dotgraphs/"]{dot2texi}
\usepackage{tikz}
\usetikzlibrary{shapes}
\usepackage{url}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{longtable}
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
\usepackage[titletoc]{appendix} % Names appendices "Appendix A"
                                % instead of just A in Contents
\usepackage[bottom]{footmisc}
\usepackage{pdfpages}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx


%\usepackage{lmodern}
\usetikzlibrary{arrows,automata}
\usepackage{verbatim}

\linespread{1.2} 
\graphicspath{{./figures/}} 

% fancy drawings
\usepackage{pgf}
\usepackage{epigraph}

% \epigraphsize{\small}% Default
\setlength\epigraphwidth{8cm}
\setlength\epigraphrule{0pt}

\usepackage{etoolbox}

\makeatletter
\patchcmd{\epigraph}{\@epitext{#1}}{\itshape\@epitext{#1}}{}{}
\makeatother

%\usepackage{boxproof}
%\usepackage{nomencl}
\usepackage{natbib}

\newcommand{\fasto}{\textsc{Fasto} }
\newcommand{\mips}{\textsc{Mips} }
\newcommand{\mars}{Mars }
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother

%-----------------------------------------------------------------------------
% HEADER AND FOOTER STUFF
%-----------------------------------------------------------------------------
\usepackage{fancyhdr}
\usepackage{lastpage} % Making it possible to write ``Page x of y'' in the footer

%\pagestyle{fancy}
%\fancyhf{}
% Header stuff below
%\lhead{Jenny-Margrethe Vej} 
%\chead{}
%\rhead{rwj935} 
% Footer stuff below
%\cfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}} % To the left at the bottom

%-----------------------------------------------------------------------------
\begin{document}
%\begin{titlepage}

\begin{center}
\textsc{\Large Smartphone Perspective on Sleeping Patterns}\\[0.5cm] 
\textsc{\large Project description}\\[0.5cm] 

%\vfill

\emph{Author:}
\\
Jenny-Margrethe \textsc{Vej} - rwj935\\ 
\vspace{10mm}

{\large \today}\\[3cm] 
\end{center}
\vspace{-20mm}

\section{Problem Statement}
First part of this project will be to research on sleep patterns in the data collected by Social 
Fabric\cite{Stopczynski2014}. This research will help us get an understanding on what kind of 
sleep data is possible to collect ourself, and we will have some data to compare with. After this 
we will conduct our own experiment on students, investigating how smartphones sees the 
students sleeping patterns. With the data from this investigation we will examine how Digital 
Cognitive Behavioural Therapy (DCBT) can be embedded in a ``intervention''. 
We expect to end up with an app for the intervention, and we will conduct another experiment
with the app to see if it is helping the students to get better sleeping patterns or not. 

\section{Motivation}
It is widely known that sleep is essential \cite{Gumbiner2012}, and sleep deprivation affects 
us in many ways. It is also commonly known that students tend to skip a few hours of sleep to 
get more out of the day. But skipping hours of sleep will most likely not do anything good - instead
students get poorer performance in school \cite{Gilbert2010}. \\

According to the central authority on Danish statistics, Statistics Denmark, every household in 
Denmark owned at least one mobilephone in 2013 \cite{DanmarksStatistik2013}, and according 
to a article in Dailymail that same year \cite{Woollaston2013}, we check our phone 110 times a 
day and up to every 6 seconds in the evening. \\

Knowing that almost everyone owns a mobilephone, and students tend to skip sleep to work more,
we thought it would be great to investigate how we can use the mobilephone to improve our 
sleeping patterns. 

\section{Elaboration}
Using already existing apps for mobilephones we will investigate students sleeping patterns over a 
time period of four weeks. When collecting the data we will also have sessions with the participants,
having them answering questionnaires and share their thoughts on the experiment so far. After the 
period is done, we will investigate the data collected and look for patterns. And based on this, we 
will create an intervention application for the mobilephones using DCBT and self-efficacy.\\

The intervention created will be tested for another period of four weeks, hopefully with the same 
students that participated in the first part. If that is not possible, we will have other students with 
a similar profile participating instead. The project will be conducted in collaboration with a psychologist 
specialised in sleep. 

\section{Learning Goals}
	\begin{itemize}
		\item 
		\item 
	\end{itemize}

%\bibliographystyle{plainnat}
\bibliographystyle{unsrt}
\bibliography{bibliography}


%-----------------------------------------------------------------------------
\end{document}